---
title: "Phylomorphospace"
output: html_document
date: "2022-08-09"
---

```{r - LIBRARIES}

library(xlsx)
library(stats)
library(rJava)
library(ape)
library(phytools)
library(png)
library(TreeTools)
library(geiger)
library(rlang)
library(pillar)
library(FactoMineR)
library(factoextra)
library(FactoClass)
library(scatterplot3d)
library(magick)
library(devtools)
library(credentials)
library(rgl)

setwd("C:/Users/Daniel/Documents/Geckolab/Data/Thesis_Analysis")

```

Some of these functions were used in generation of an RGL object for the 3D morphospace later on

```{r - Functions}

rgl_init <- function(new.device = FALSE, bg = "white", width = 640) { 
  if( new.device | rgl.cur() == 0 ) {
    rgl.open()
    par3d(windowRect = 50 + c( 0, 0, width, width ) )
    rgl.bg(color = bg )
  }
  rgl.clear(type = c("shapes", "bboxdeco"))
  rgl.viewpoint(theta = 15, phi = 20, zoom = 0.7)
}

rgl_add_axes <- function(x, y, z, axis.col = "grey",
                xlab = "", ylab="", zlab="", show.plane = TRUE, 
                show.bbox = FALSE, bbox.col = c("#333377","black"))
  { 
  
  lim <- function(x){c(-max(abs(x)), max(abs(x))) * 1.1}
  # Add axes
  xlim <- lim(x); ylim <- lim(y); zlim <- lim(z)
  rgl.lines(xlim, c(0, 0), c(0, 0), color = axis.col)
  rgl.lines(c(0, 0), ylim, c(0, 0), color = axis.col)
  rgl.lines(c(0, 0), c(0, 0), zlim, color = axis.col)
  
   # Add a point at the end of each axes to specify the direction
   axes <- rbind(c(xlim[2], 0, 0), c(0, ylim[2], 0), 
                 c(0, 0, zlim[2]))
   rgl.points(axes, color = axis.col, size = 3)
  
  # Add axis labels
  rgl.texts(axes, text = c(xlab, ylab, zlab), color = axis.col,
             adj = c(0.5, -0.8), size = 2)
  
  # Add plane
  if(show.plane) 
    xlim <- xlim/1.1; zlim <- zlim /1.1
    rgl.quads( x = rep(xlim, each = 2), y = c(0, 0, 0, 0),
             z = c(zlim[1], zlim[2], zlim[2], zlim[1]))
  
  # Add bounding box decoration
  if(show.bbox){
    rgl.bbox(color=c(bbox.col[1],bbox.col[2]), alpha = 0.5, 
          emission=bbox.col[1], specular=bbox.col[1], shininess=5, 
          xlen = 3, ylen = 3, zlen = 3) 
  }
}

get_colors <- function(groups, group.col = palette()){
  groups <- as.factor(groups)
  ngrps <- length(levels(groups))
  if(ngrps > length(group.col)) 
    group.col <- rep(group.col, ngrps)
  color <- group.col[as.numeric(groups)]
  names(color) <- as.vector(groups)
  return(color)
}

lim <- function(x){c(-max(abs(x)), max(abs(x))) * 1.1}

```

Read in data.
Excel spreadsheet was created by copying over character states from Mesquite Character Matrix.
Tree is obtained from Pyron et al. 2015 (https://link.springer.com/article/10.1186/1471-2148-13-93) and was coerced into an appropriate Newick format using FigTree after taxa not present in my sample were pruned.
Characters are available in the Thesis or Combined_Data_Tree Mesquite dataset.

```{r - DATA}

#Read in newick tree from Pyron 2013
pyron <- read.tree("Scale_NEWICK.phy")

#Read in dataset from excel
scale <- as.matrix(read.xlsx('Dataset.xlsx',
                             sheetIndex = 1,
                             rowIndex = 1:153,
                             colIndex = 2:181,
                             header = F))
#Return taxa names
scale_taxa <- read.xlsx('Dataset.xlsx',
                   sheetIndex = 1,
                   rowIndex = 1:153,
                   colIndex = 1,
                   as.data.frame = F)
#Develop vector for denoting proper character numbers
ch <- c(1:180)
#Apply names to each section of the matrix
rownames(scale) <- scale_taxa
colnames(scale) <- ch

#Verify that taxa are identically named
name.check(pyron, scale)
#Underscores instead of spaces in our tree, data needs to be changed
rownames(scale) <- gsub(" ","_",rownames(scale))
#Now to verify
name.check(pyron, scale)

#Set up the data to use in MCA
scale.df <- as.data.frame(scale)
#Naming variables will help with interpretation later on
var_names <- (c("Rostral", "Ex.Rostral", "Spl.Rostral", "Narial.Op", "Op.Rostral", "Op.Superlab",
                "Nasal.Ros", "Supralab.Ros", "Internasal", "Ceph.Size", "Ceph.Keel", "Ceph.Elong",
                "En.Frontal", "FParietal.Con", "CirOrbital", "En.Supraoc", "Supraoc.Row", "Supracil",
                "Supraoc.Con", "Supracil.Ov", "Supralab.Orb", "En.Suboc", "Suboc.Con", "En.Interpar",
                "En.Temp", "Heat.Pit", "Mouth", "Tongue.Gr", "Eye", "Eye.Scales",
                "Eyelids", "Low.Eye.Sc", "Spectacle", "Gran.Eyelid", "Ear", "Tympanum",
                "Ear.Cover", "Dewlap", "Mental", "El.Postment", "One.Postment", "En.Med.Infralab",
                "Infralab.Sep", "Ex.Labials", "Mental.Gr", "Gular.Fold", "Annul.Body", "Varanus.Sc",
                "Homo.Dorsal", "Gen.Dorsal", "Body.Keel", "Dorsal.Ridge", "En.Middorsal", "Nuchal.Cr",
                "Gen.Lateral", "Lateral.Fold", "Gastrosteges", "Ventral.Size", "Gen.Ventral", "Belly.Keel",
                "Ventral.Edge", "Fem.Pores", "Preanal.Pores", "Tail.Tip", "Tail.Spike", "Tail.Cross",
                "Tail.Size", "Tail.Keel", "Annul.Tail", "En.Preanal", "Anal.Plate", "En.Postanal",
                "Tubercles", "One.Subcaudal", "Ex.Hindlimb", "Limb.Cross", "Toe.Pads", "Subdig.Num",
                "Subdig,Keel", "Mittens", "Claw.Sheath", "Frontal.Shape", "Frontal.Tex", "Frontal.Ov",
                "Chalcidine", "Inasal.Shape", "Inasal.Tex", "Inasal.Keel", "Inasal.K.T", "Loreal.Shape",
                "Loreal.Tex", "Loreal.Keel", "Loreal.K.T", "Loreal.Just", "Loreal.Ov", "En.Loreal",
                "Supraoc.Shape", "Supraoc.Tex", "Supraoc.Keel", "Supraoc.K.T", "Supraoc.Just", "Supraoc.Ov",
                "Postmen.Shape", "Postmen.Tex", "Postmen.Keel", "Postmen.K.T", "Postmen.Ov", "Homo.DNeck",
                "DNeck.Shape", "DNeck.Tex", "DNeck.Keel", "DNeck.K.T", "DNeck.Just", "DNeck.Ov",
                "LNeck.Shape", "LNeck.Tex", "LNeck.Keel", "LNeck.K.T", "LNeck.Just", "LNeck.Ov",
                "VNeck.Shape", "VNeck.Tex", "VNeck.Keel", "VNeck.K.T", "VNeck.Just", "VNeck.Ov",
                "Dorsal.Shape", "Dorsal.Tex", "Dorsal.Keel", "Dorsal.K.T", "Dorsal.Just", "Dorsal.Ov",
                "Lateral.Shape", "Lateral.Tex", "Lateral.Keel", "Lateral.K.T", "Lateral.Just", "Lateral.Ov",
                "Ventral.Shape", "Ventral.Tex", "Ventral.Keel", "Ventral.K.T", "Ventral.Just", "Ventral.Ov",
                "Thigh.Shape", "Thigh.Tex", "Thigh.Keel", "Thigh.K.T", "Thigh.Just", "Thigh.Ov",
                "Foot.Shape", "Foot.Tex", "Foot.Keel", "Foot.K.T", "Foot.Just", "Foot.Ov",
                "Digit.Just", "Digit.Ov", "DCaudal.Shape", "DCaudal.Tex", "DCaudal.Keel", "DCaudal.K.T",
                "DCaudal.Just", "DCaudal.Ov", "VCaudal.Shape", "VCaudal.Tex", "VCaudal.Keel", "VCaudal.K.T",
                "VCaudal.Just", "VCaudal.Ov", "Ap.Pits", "Osteoderms", "Spines", "Horns",
                "Subtympanic", "Supraoc.Disc", "Sens.Head", "Sens.Body", "Scale.Form", "Mid.Ven.Crest"))
colnames(scale.df) <- var_names

```



```{r - Run All Data}

#Generate groups, starting with clades
clade <- c("Sphenodon", "Dibamidae", (rep("Gekkota", 20)), (rep("Scincoidea", 16)), (rep("Teioidea", 8)),
           (rep("Amphisbaenia", 8)), (rep("Lacertoidea", 4)), (rep("Anguimorpha", 15)),
           (rep("Acrodonta", 7)), (rep("Pleurodonta", 28)), (rep("'Scolecophidia'", 7)),
           (rep("Alethinophidia", 38)))

#Use multiple correspondence analysis
scale.MCA <- MCA(scale.df, axes = c(1,2), na.method = "NA", graph = F)

#Some extra visualization may be possible but is not necessary

#scale.MCA$ind
#scale.MCA$var
#plot.MCA(scale.MCA, axes = c(1,2), choix = "ind",invisible = "var", )
#plot.MCA(scale.MCA, axes = c(1,2), choix = "var",invisible = "ind", )

#Visualize separation in individuals along these axes
grp.clade <- as.factor(clade)
fviz_mca_ind(scale.MCA,
             label = "none",
             habillage = grp.clade,
             palette = c("#AA4466", "#88CCEE", "#CC6677", "#999933",
                         "#DDCC77", "#6699CC", "#882255", "#AA4499",
                         "#44AA99", "#117733", "#661100", "#332288"),
             cex = 5,
             ggtheme = theme_minimal()
             )

#Contribution shows that limbless traits are skewing data potentially
fviz_mca_var(scale.MCA,
             label = "none",
             col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = T,
             ggtheme = theme_minimal()
             )

```

Now to rerun the analyses without the limbless characters. This may be a bit more informative, and could show some separation in the body scales a bit more. Currently the analysis is assuming all of the "?" characters indicate shared states for snakes, amphisbaenians, and other limbless taxa despite there simply being absent info.

```{r - Limb Corrected Data}

#Remove limb dependent characters from dataset
scale.body <- subset(scale.df,
                     select = -c(145:158))
scale.body <- subset(scale.body,
                     select = -c(75:81))

#Run MCA
scale.body.MCA <- MCA(scale.body, axes = c(1,2), na.method = "NA", graph = F)
scale.body.MCA2 <- MCA(scale.body, axes = c(2,3), na.method = "NA", graph = F)

#scale.body.MCA$ind
#scale.body.MCA$var
#plot.MCA(scale.body.MCA, axes = c(1,2), choix = "ind", invisible = "var")

#Identify contribution of key characters
fviz_contrib(scale.body.MCA, choice = "var", axes = 1, top = 15)
fviz_contrib(scale.body.MCA, choice = "var", axes = 2, top = 15)
#And both axes together
fviz_contrib(scale.body.MCA, choice = "var", axes = 1:2, top = 15)
#It appears overlap and justification are key contributors to variance

#Visualize separation in individuals without limbed characters, used png() to save high resolution images
#png(filename = "HiRes2_1.5pt.png", res = 800, width = 5000, height = 3200)

fviz_mca_ind(scale.body.MCA,
             label = "none",
             habillage = grp.clade,
             palette = c("#e66c76", "#88CCEE", "#cc7f43", "#999933",
                         "#DDCC77", "#6699CC", "#8a000b", "#d41cce",
                         "#44AA99", "#117733", "#2f3d34", "#332288"),
             #addEllipses = T, ellipse.level = 0.95,
             #select.ind = list(contrib = 68),
             shape.ind = "triangle",
             pointsize = 1.5,
             invisible = "quali",
             ggtheme = theme_minimal()
             )

#Develop a vector for lizards
scale_lizards <- scale.body[-c(109:153), ]

#Now the other two axes, with Dim 2 on the Y
#png(filename = "Final_Ellipses_12_1.5.png", res = 800, width = 5000, height = 3200)

fviz_mca_ind(scale.body.MCA,
             axes = c(1, 2),
             label = "none",
             habillage = grp.clade,
             palette = c("#4ccf84", "#e66c76", "#117733", "#8fc2db", "#cc7f43", "#999933",
                         "#DDCC77", "#2b95ff", "#8a000b", "#d41cce",
                         "#2f3d34", "#332288"),
             addEllipses = T, ellipse.level = 0.95,
             #select.ind = list(name = rownames(scale_lizards)),
             shape.ind = "triangle",
             pointsize = 1.5,
             invisible = "quali",
             ggtheme = theme_minimal()
             )


#Visualize Variable directionality
#png(filename = "HiRes2_Var_12_Names_Test.png", res = 800, width = 9000, height = 3200)

fviz_mca_var(scale.body.MCA,
             #label = "none",
             axes = c(1, 2),
             col.var = "contrib",
             gradient.cols = c("#91008d", "#00d420"),
             #alpha.var = "cos2",
             #repel = T,
             select = list(contrib = 20),
             geom.var = c("arrow", "text"),
             ggtheme = theme_minimal()
             )


```

Not that this is necessary, but I wanted to visualize what would happen if several (presumably) uninformative characters were removed. This ended up having little bearing on the percent of variation explained by the top three taxa thus it was not necessary.

```{r - Minimizing MCA Variables}

scale.min <- subset(scale.body,
                    select = -c(82, 86, 93, 99, 105, 111, 117, 123, 129, 135, 141, 147),
                    drop = T)

min.MCA <- MCA(scale.min, axes = c(1, 2), na.method = "NA", graph = F)

#Visualize separation in individuals without limbed characters
fviz_mca_ind(min.MCA,
             label = "none",
             habillage = grp.clade,
             palette = c("#AA4466", "#88CCEE", "#CC6677", "#999933",
                         "#DDCC77", "#6699CC", "#882255", "#AA4499",
                         "#44AA99", "#117733", "#661100", "#332288"),
             #addEllipses = T, ellipse.level = 0.95,
             #select.ind = list(contrib = 68),
             cex = 5,
             pointsize = 4.5,
             invisible = "quali",
             ggtheme = theme_minimal()
             )

```


Various examples of variable contribution using package FactoExtra

```{r - Visualize Variable Contribution}

fviz_contrib(scale.MCA, choice = "var", axes = 1, top = 15)
fviz_contrib(scale.body.MCA, choice = "var", axes = 1, top = 15)

#png(filename = "HiRes_Contribution.png", res = 800, width = 8000, height = 3200)

fviz_contrib(MCA.3D, choice = "var", axes = 1:3, top = 40)

fviz_mca_var(scale.MCA, choice = "mca.cor",
             repel = T)
fviz_mca_var(scale.body.MCA, choice = "mca.cor",
             col.var = "contrib",
             repel = T)
fviz_mca_var(min.MCA, choice = "mca.cor",
             repel = T)
fviz_mca_var(MCA.3D, choice = "mca.cor",
             repel = T,
             col.var = "black",
             shape.var = 16)+
  scale_color_gradient2(low = "steelblue", mid = "blue", high = "orange", midpoint = 0.5)

```





Some of these vectors were generated to visualize only certain clades at a time. Not necessary

```{r - Preparing specific Figures}

#Visualize limb reduced groups
knubs <- list(name = c("Xantusia_vigilis", "Lepidophyma_pajapanensis", "Gerrhosaurus_sp", "Gerrhosaurus_flavigularis",
                       "Platysaurus_intermedius", "Smaug_warreni", "Plestiodon_obsoletus", "Plestiodon_fasciatus", "Scincella_lateralis",
                       "Tribolonotus_novaeguineae", "Tiliqua_sp", "Tiliqua_scincoides", "Tiliqua_gigas", "Trachylepis_sp",
                       "Rhineura_floridana", "Bipes_canaliculatus", "Blanus_alexandri", "Cadea_blanoides", "Trogonophis_wiegmanni",
                       "Amphisbaena_mertensii", "Amphisbaena_camura", "Leposternon_microcephalum", "Helminthophis_frontalis", "Trilepida_macrolepis",
                       "Rena_humilis", "Gerrhopilus_persephone", "Xenotyphlops_grandidieri", "Typhlops_reticulatus", "Typhlops_hectus",
                       "Anilius_scytale", "Tropidophis_spiritus", "Xenophidion_acanthognathus", "Casarea_dussumieri", "Exiliboa_placata",
                       "Corallus_caninus", "Anomochilus_monticola", "Cylindrophis_ruffus", "Uropeltis_melanogaster", "Xenopeltis_unicolor",
                       "Loxocemus_bicolor", "Python_brongersmai", "Python_sebae", "Acrochordus_javanicus", "Achalinus_juliani", "Aplopeltura_boa",
                       "Bitis_caudalis", "Trimeresurus_venustus", "Crotalus_stephensi", "Crotalus_cerastes", "Crotalus_molossus", "Crotalus_tigris",
                       "Enhydris_enhydris", "Atractaspis_irregularis", "Micrurus_tener", "Ophiophagus_hannah", "Laticauda_colubrina",
                       "Hapsidophrys_smaragdina", "Tantilla_cucullata", "Leptophis_ahaetulla", "Drymobius_margaritiferus", "Masticophis_lateralis",
                       "Xenochrophis_vittatus", "Tropidodipsas_sartorii", "Sibynomorphus_turgidus", "Borikenophis_portoricensis"))

#Visualize Toxicoferan lizards
toxic <- list(name = c("Xenosaurus_grandis", "Heloderma_suspectum", "Anniella_geronimensis", "Anniella_pulchra", "Ophiodes_luciae",
                       "Ophisaurus_attenuatus", "Mesaspis_monticola", "Abronia_ornelasi", "Shinisaurus_crocodilurus", "Lanthanotus_borneensis",
                       "Varanus_sp", "Chamaeleo_calyptratus", "Trioceros_jacksonii", "Uromastyx_aegyptia", "Uromastyx_ocellata", "Moloch_horridus",
                       "Pogona_vitticeps", "Acanthosaura_capra", "Uranoscodon_superciliosus", "Plica_plica", "Iguana_iguana", "Sauromalus_obesus",
                       "Ctenosaura_similis", "Leiocephalus_carinatus", "Crotaphytus_bicinctores", "Crotaphytus_collaris", "Holbrookia_maculata",
                       "Phrynosoma_cornutum", "Sceloporus_sp", "Hoplocercus_spinosus", "Enyalioides_laticeps", "Enyalioides_palpebralis",
                       "Oplurus_cuvieri", "Anisolepis_grilli", "Liolaemus_rothi", "Basiliscus_basiliscus", "Basiliscus_plumifrons",
                       "Anolis_carolinensis", "Anolis_evermanni", "Anolis_stratulus", "Anolis_pulchellus", "Anolis_gundlachi",
                       "Anolis_cristatellus", "Anolis_sagrei", "Anolis_sp"))

#Now with snakes
toxic_plus <- list(name = c("Xenosaurus_grandis", "Heloderma_suspectum", "Anniella_geronimensis", "Anniella_pulchra", "Ophiodes_luciae",
                       "Ophisaurus_attenuatus", "Mesaspis_monticola", "Abronia_ornelasi", "Shinisaurus_crocodilurus", "Lanthanotus_borneensis",
                       "Varanus_sp", "Chamaeleo_calyptratus", "Trioceros_jacksonii", "Uromastyx_aegyptia", "Uromastyx_ocellata", "Moloch_horridus",
                       "Pogona_vitticeps", "Acanthosaura_capra", "Uranoscodon_superciliosus", "Plica_plica", "Iguana_iguana", "Sauromalus_obesus",
                       "Ctenosaura_similis", "Leiocephalus_carinatus", "Crotaphytus_bicinctores", "Crotaphytus_collaris", "Holbrookia_maculata",
                       "Phrynosoma_cornutum", "Sceloporus_sp", "Hoplocercus_spinosus", "Enyalioides_laticeps", "Enyalioides_palpebralis",
                       "Oplurus_cuvieri", "Anisolepis_grilli", "Liolaemus_rothi", "Basiliscus_basiliscus", "Basiliscus_plumifrons",
                       "Anolis_carolinensis", "Anolis_evermanni", "Anolis_stratulus", "Anolis_pulchellus", "Anolis_gundlachi",
                       "Anolis_cristatellus", "Anolis_sagrei", "Anolis_sp", "Helminthophis_frontalis", "Trilepida_macrolepis",
                       "Rena_humilis", "Gerrhopilus_persephone", "Xenotyphlops_grandidieri", "Typhlops_reticulatus", "Typhlops_hectus",
                       "Anilius_scytale", "Tropidophis_spiritus", "Xenophidion_acanthognathus", "Casarea_dussumieri", "Exiliboa_placata",
                       "Corallus_caninus", "Anomochilus_monticola", "Cylindrophis_ruffus", "Uropeltis_melanogaster", "Xenopeltis_unicolor",
                       "Loxocemus_bicolor", "Python_brongersmai", "Python_sebae", "Acrochordus_javanicus", "Achalinus_juliani", "Aplopeltura_boa",
                       "Bitis_caudalis", "Trimeresurus_venustus", "Crotalus_stephensi", "Crotalus_cerastes", "Crotalus_molossus", "Crotalus_tigris",
                       "Enhydris_enhydris", "Atractaspis_irregularis", "Micrurus_tener", "Ophiophagus_hannah", "Laticauda_colubrina",
                       "Hapsidophrys_smaragdina", "Tantilla_cucullata", "Leptophis_ahaetulla", "Drymobius_margaritiferus", "Masticophis_lateralis",
                       "Xenochrophis_vittatus", "Tropidodipsas_sartorii", "Sibynomorphus_turgidus", "Borikenophis_portoricensis"))

```

Actual ellipse figure generation with above categories.

```{r - Figure Generation}

#Limb reduced clades
fviz_mca_ind(min.MCA, title = "Limb Reduced Clades",
             label = "none",
             #repel = T,
             habillage = grp.clade,
             palette = c("#88CCEE", "#AA4499", "#44AA99", "#117733"),
             select.ind = knubs,
             addEllipses = T, ellipse.level = 0.95,
             cex = 10,
             pointsize = 4.5,
             invisible = "quali",
             ggtheme = theme_minimal(),
             )

#Toxicoferan lizards
fviz_mca_ind(min.MCA, title = "Toxicoferan Lizards",
             label = "none",
             #repel = T,
             habillage = grp.clade,
             palette = c("#DDCC77", "#332288", "#882255"),
             select.ind = toxic,
             addEllipses = T, ellipse.level = 0.95,
             cex = 10,
             pointsize = 4.5,
             invisible = "quali",
             ggtheme = theme_minimal(),
             )

#All toxicofera
fviz_mca_ind(min.MCA, title = "Toxicofera",
             label = "none",
             #repel = T,
             habillage = grp.clade,
             palette = c("#DDCC77", "#332288", "#882255", "#44AA99", "#117733"),
             select.ind = toxic_plus,
             addEllipses = T, ellipse.level = 0.95,
             cex = 10,
             pointsize = 4.5,
             invisible = "quali",
             ggtheme = theme_minimal(),
             )

```




Now to place all three axes on the same scatterplot. This is not a capability of FactoMineR or FactoExtra, thus I had to make a workaround by isolating the coordinates and running them through either package rgl or scatterplot3d. Because there are many ways to go about this I have each method separated by a block of code.

```{r - 3D MCA}
#Get 3 Dimensional MCA
MCA.3D <- MCA(scale.body, ncp = 3, na.method = "NA")
coords <- MCA.3D$ind$coord
coords <- as.data.frame(coords)

#Set up groups for visualizing differences in 3D plot
color_3d <- c("#AA4466", "#88CCEE", (rep("#CC6677", 20)), (rep("#999933", 16)),
              (rep("#DDCC77", 8)), (rep("#6699CC", 8)), (rep("#882255", 4)), (rep("#AA4499", 15)),
              (rep("#44AA99", 7)), (rep("#117733", 28)), (rep("#661100", 7)), 
              (rep("#332288", 38)))

#Empty plot for points3d()
s3d <- scatterplot3d(coords$`Dim 1`, coords$`Dim 2`, coords$`Dim 3`,
                     pch = "",
                     grid = F, box = F)


#Using RGL to generate a 3D scatterplot
rgl_init()
rgl.bg(color = "white")
rgl.spheres(coords$`Dim 1`, coords$`Dim 2`, coords$`Dim 3`,
            r = 0.030, color = get_colors(color_3d, c("#8a000b", "#117733", "#e66c76", "#44aa99",
                                                      "#88ccee", "#6699cc", "#918716", "#d41cce",
                                                      "#2f3d34", "#cc7f43", "#ddcc77", "#332288"
                                                     )))
rgl.lines(lim(coords$`Dim 1`), c(0, 0), c(0, 0), color = "black")
rgl.lines(c(0, 0), lim(coords$`Dim 2`), c(0, 0), color = "red")
rgl.lines(c(0, 0), c(0, 0), lim(coords$`Dim 3`), color = "green")
#rgl_add_axes(coords$`Dim 1`, coords$`Dim 2`, coords$`Dim 3`,
             #show.bbox = T)
rgl.bbox(color = c("white", "black"), emission = "white",
         specular = "#7a7a7a", shininess = 3, alpha = 0.75)
aspect3d(1,1,1)

```


```{r}

plot3d(coords$`Dim 1`, coords$`Dim 2`, coords$`Dim 3`,
       xlab = "Dimension 1", ylab = "Dimension 2", zlab = "Dimension 3",
       type = "s", col = get_colors(color_3d, c("#8a000b", "#117733", "#e66c76", "#4ccf84",
                                                      "#8fc2db", "#2b95ff", "#918716", "#d41cce",
                                                      "#2f3d34", "#cc7f43", "#ddcc77", "#332288"
                                                     )),  
        radius = 0.80, add = FALSE)
aspect3d(20, 20, 20)

rgl.snapshot(filename = "Final3D5.png")

#Write a gif of the morphospace
movie3d(spin3d(axis = c(0, 1, 0)), duration = 10,
        dir = getwd())


```

Here I considered adjusting the axes size to represent the variation explained by that eigenvalue... This not only turned out to be difficult to represent well but may not have really given the impression I wanted. I left this code alone in case I want to come back to it.

```{r - 3D MCA}

#Scale to variation explained?
rgl_init()
rgl.bg(color = "white")
rgl.spheres(coords$`Dim 1`, coords$`Dim 2`, coords$`Dim 3`,
            r = 0.025, color = get_colors(color_3d, c("#4f0000", "#117733", "#7d4a4a", "#61ff6b",
                                                      "#6699CC", "#5cf2f2", "#b8ff6b", "#603b7d",
                                                      "#ff3838", "#f79c2d", "#ffed99", "#202496"
                                                     )))
rgl_add_axes(coords$`Dim 1`, coords$`Dim 2`, coords$`Dim 3`,
             show.bbox = T)
rgl.bbox(color = c("black", "black"), emission = "black",
         specular = "#7a7a7a", shininess = 3, alpha = 0.75)
aspect3d()

```

Scatterplot3d can be powerful for adding legends and other tools for visualization, but ended up being too much of a nightmare to orient correctly. Code is left here for the same reason as above.

```{r - 3D Figure Generation}

#NEED TO FIX: NAMES ARE NOT IN THE PROPER SPACE

#And legend
legend <- c("Rhynchocephalia", "Dibamidae", "Gekkota", "Scincoidea",
            "Teioidea", "Amphisbaenia", "Lacertoidea", "Anguimorpha",
            "Acrodonta", "Pleurodonta", "Scolecophidia", "Serpentes")
#And color palette for legend
legend.col <- c(
  #Rhynch
  "#e30000",
  #Dib
  "#999933",
  #Gekk
  "#DDCC77",
  #Scin
  "#8b11b8",
  #Teiid
  "#332288",
  #Amph
  "#88CCEE",
  #Lacer
  "#6699CC",
  #Angui
  "#ff9421",
  #Acro
  "#75041a",
  #Pleuro
  "#b84d62",
  #Scol
  "#44AA99",
  #Serp
  "#117733")

color_3d_plot <- c("#e30000", "#999933", (rep("#DDCC77", 20)), (rep("#8b11b8", 16)),
              (rep("#332288", 8)), (rep("#88CCEE", 8)), (rep("#6699CC", 4)), (rep("#ff9421", 15)),
              (rep("#75041a", 7)), (rep("#b84d62", 28)), (rep("#44AA99", 7)), 
              (rep("#117733", 38)))

scatterplot3d(coords$`Dim 1`, coords$`Dim 2`, coords$`Dim 3`,
              angle = 20,
              type = "h",
              xlab = "Dimension 1 (%)",
              ylab = "Dimension 2 (%)",
              zlab = "Dimension 3 (%)",
              pch = 19,
              grid = F, box = F,
              color = color_3d_plot)
addgrids3d(coords$`Dim 1`, coords$`Dim 2`, coords$`Dim 3`, grid = c("xy", "xz", "yz"),
           angle = 20)
s3d$points3d(coords$`Dim 1`, coords$`Dim 2`, coords$`Dim 3`,
             pch = 16,
             cex = 2,
             col = color_3d_plot)
legend("bottom", legend = legend,
       col = legend.col, pch = 16,
       #inset = 0.25,
       xpd = T)

```

Again, I thought it may be interesting to only use the characters that contributed most to the variation. This showed little effect on % explained by each axis and ultimately lowered the resolution. Those additional 100+ characters offer small insights and differences between similar families or genera.

```{r - Highest Contribution Characters Only}

#Read in data
scale.red <- as.matrix(read.xlsx('Char_Reduction.xlsx',
                             sheetIndex = 1,
                             rowIndex = 1:153,
                             colIndex = 2:71,
                             header = F))
scale.red <- as.data.frame(scale.red)

#Name 70 Variables, fix column and row names
red_names <- (c("Narial.Op", "Nasal.Ros", "Supralab.Ros", "Internasal", "Ceph.Size", "Ceph.Keel", "Supraoc.Row", "Supracil",
                "Supraoc.Con", "Suboc.Con", "En.Interpar", "Tongue.Gr", "Eye", "Eye.Scales", "Low.Eye.Sc", "Tympanum",
                "Annul.Body", "Gen.Body", "Gen.Lateral", "Gastrosteges", "Belly.Keel", "Tail.Cross", "Tail.Keel", "Annul.Tail",
                "En.Preanal", "Anal.Plate", "Frontal.Shape", "Frontal.Ov", "Chalcidine", "Loreal.Keel", "Loreal.Ov", "Supraoc.Shape",
                "Supraoc.Tex", "Supraoc.Keel", "Supraoc.Just", "Supraoc.Ov", "Postmen.Ov", "DNeck.Shape", "DNeck.Tex",
                "DNeck.Just", "DNeck.Ov", "LNeck.Tex","LNeck.Just", "LNeck.Ov", "VNeck.Shape", "VNeck.Tex", "VNeck.Just",
                "VNeck.Ov", "Dorsal.Shape", "Dorsal.Tex", "Dorsal.Just", "Dorsal.Ov", "Lateral.Shape", "Lateral.Tex",
                "Lateral.Just", "Lateral.Ov", "Ventral.Shape", "Ventral.Tex", "Ventral.Keel", "Ventral.K.T", "DCaudal.Shape",
                "DCaudal.Keel", "DCaudal.K.T", "DCaudal.Just", "DCaudal.Ov", "VCaudal.Keel", "VCaudal.Just", "VCaudal.Ov",
                "Osteoderms", "Supraoc.Disc"))
colnames(scale.red) <- red_names
rownames(scale.red) <- scale_taxa

#Run MCA
red.MCA <- MCA(scale.red, axes = c(1, 2), na.method = "NA", graph = F)

#Character reduction MCA plot
fviz_mca_ind(red.MCA,
             label = "none",
             habillage = grp.clade,
             palette = c("#AA4466", "#88CCEE", "#CC6677", "#999933",
                         "#DDCC77", "#6699CC", "#882255", "#AA4499",
                         "#44AA99", "#117733", "#661100", "#332288"),
             #addEllipses = T, ellipse.level = 0.95,
             #select.ind = list(contrib = 68),
             cex = 5,
             pointsize = 4.5,
             invisible = "quali",
             ggtheme = theme_minimal()
             )

#3D Plot
#Get 3 Dimensional MCA
red.3d <- MCA(scale.red, ncp = 3, na.method = "NA")
coords.red <- red.3d$ind$coord
coords.red <- as.data.frame(coords.red)

#Using RGL to generate a 3D scatterplot
rgl_init()
rgl.bg(color = "white")
rgl.spheres(coords.red$`Dim 1`, coords.red$`Dim 2`, coords.red$`Dim 3`,
            r = 0.025, color = get_colors(color_3d, c("#4f0000", "#117733", "#7d4a4a", "#61ff6b",
                                                      "#6699CC", "#5cf2f2", "#b8ff6b", "#603b7d",
                                                      "#ff3838", "#f79c2d", "#ffed99", "#202496"
                                                     )))
rgl.lines(lim(coords.red$`Dim 1`), c(0, 0), c(0, 0), color = "black")
rgl.lines(c(0, 0), lim(coords.red$`Dim 2`), c(0, 0), color = "red")
rgl.lines(c(0, 0), c(0, 0), lim(coords.red$`Dim 3`), color = "green")
#rgl_add_axes(coords$`Dim 1`, coords$`Dim 2`, coords$`Dim 3`,
             #show.bbox = T)
rgl.bbox(color = c("black", "black"), emission = "black",
         specular = "#7a7a7a", shininess = 3, alpha = 0.75)
aspect3d(1,1,1)

```

A phylomorphospace can be generated using only the 2D morphospace coordinates. It doesn't offer much insight by itself, at least that can't already be observed by grouping taxa into higher level relationships on the above 3D morphospaces. A 3D phylomorphospace could be interesting, but is beyond my R capabilities right now.

```{r - The Phylomorphospace}

phylomorphospace(pyron, scale.body.MCA$ind$coord,
                 label = F,
                 #direction = "from",
                 xlab = "Dimension 1 (12%)", ylab = "Dimension 2 (5.3%)")

```




























































